\LARGE \bf Mixed Non-Bayesian and DeGroot Learning

### 2012-12-12 docs/paper.tex
Fixed lowercase fig reference

The results, shown in figure~\ref{fig:convergence_time}, show that time required for convergence appears to be linear with respect to the number of nodes in the graph.

>>>>

The results, shown in Figure~\ref{fig:convergence_time}, show that time required for convergence appears to be linear with respect to the number of nodes in the graph.
